---
title: "p8105_hw6_yw3236"
output: github_document
author: "Yishan Wang"
date: "2018-11-19"
---

# Problem 1

```{r include = FALSE}
library(tidyverse)
library(modelr)
```

```{r}
homicides_data = read.csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
```

```{r}
new_homicides_data = homicides_data %>%
  mutate(city_state = paste(city, state, sep = ", ")) %>%
  mutate(resolved = as.numeric(disposition == "Closed by arrest")) %>% #factor???
  filter(city_state != "Dallas, TX" & city_state != "Phoenix, AZ" & city_state != "Kansas City, MO") %>%
  filter(city_state != "Tulsa, AL") %>%
  mutate(victim_race = ifelse(victim_race == "White", "white", "non-white"),
         victim_race = fct_relevel(victim_race, "white"),
         victim_age = as.numeric(victim_age))
```

```{r}
fit_logistic = new_homicides_data %>%
  filter(city_state == "Baltimore, MD") %>%
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 
```

```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         CI_lower = exp(estimate - qnorm(0.975) * std.error),
         CI_upper = exp(estimate + qnorm(0.975) * std.error)) %>%
  filter(term == "victim_racenon-white") %>%
  select(OR, CI_lower, CI_upper, p.value) %>% 
  knitr::kable(digits = 3)
```

```{r}
glm_function = function(city_data){
  
  city_data %>%
    nest(-city_state) %>%  #nest first
    mutate(glm = purrr::map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())),
           tidied = purrr::map(glm, broom::tidy)) %>%  #apply test
    unnest(tidied, .drop = TRUE) %>%  #unnest
    mutate(OR = exp(estimate),
           CI_lower = exp(estimate - qnorm(0.975) * std.error),
           CI_upper = exp(estimate + qnorm(0.975) * std.error)) %>%
    filter(term == "victim_racenon-white") %>%
    select(city_state, OR, CI_lower, CI_upper, p.value) %>%
    data.frame()
  
}
```

```{r}
multicity_glm = glm_function(new_homicides_data)

multicity_glm
```

```{r warning = FALSE}
multicity_glm %>%
  ggplot() +
  geom_point(aes(x = reorder(city_state, OR), y = OR)) +  #order cities by the value of estimates
  geom_errorbar(aes(x = reorder(city_state, OR), ymin = CI_lower, ymax = CI_upper, OR)) +  #add error bar
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = rel(1))) +
  labs(x = "City", y = "OR Comparing Non-white Victims to White Victims (95% CI)")
```

# Problem 2

Load and clean the data for regression analysis:
* convert numeric to factor where appropriate
* check for missing data

```{r}
birthweight_data = read.csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(mrace = factor(mrace, levels = c("1", "2", "3", "4", "8")),
         malform = factor(malform, levels = c("0", "1")),
         frace = factor(frace, levels = c("1", "2", "3", "4", "8", "9")),
         babysex = factor(babysex, levels = c("1", "2")))

sapply(birthweight_data, function(x)sum(is.na(x)))  #no missing data
```

Modeling process:

```{r}
# Explorations: pairwise correlations to identify collinearity 
Hmisc::rcorr(as.matrix(birthweight_data)) %>%
  broom::tidy() %>%
  mutate(abs_estimate = abs(estimate)) %>%
  filter(abs_estimate >= 0.5)
```

```{r}
# Fit a regression using all predictors except `pnumlbw` and `pnumsga`
mult.fit = lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + ppbmi + ppwt + smoken + wtgain, data = birthweight_data)
summary(mult.fit)

# Backward selection
# Remove wtgain
step1 = update(mult.fit, . ~ . -wtgain)
summary(step1)

# Remove malform
step2 = update(step1, . ~ . -malform)
summary(step2)

# Remove frace
step3 = update(step2, . ~ . -frace)
summary(step3)

# Remove ppbmi
step4 = update(step3, . ~ . -ppbmi)
summary(step4)

# Remove momage
step5 = update(step4, . ~ . -momage)
summary(step5)

# Remove menarche
step6 = update(step5, . ~ . -menarche)
summary(step6)

# Remove fincome
step7 = update(step6, . ~ . -fincome)
summary(step7)

# Remove parity
step8 = update(step7, . ~ . -parity)
summary(step8)

# Remove colinearity (bhead or blength)

step9 = update(step8, . ~ . -bhead)
summary(step9)

step9 = update(step8, . ~ . -blength)
summary(step9)
# Since deleting either bhead or blength results significant decreasing in both adjusted R-squared and multiple R-squared, I choose to keep both behead and blength. Although behead and blength have linear relationship, it's not the strong linear relationship.

# Remove colinearity (delwt or ppwt)

step10 = update(step8, . ~ . -delwt)
summary(step10)

step_10 = update(step8, . ~ . -ppwt)
summary(step10)
# Since deleting ppwt results less decreasing in both adjusted R-squared and multiple R-squared, I choose to move ppwt.

porposed_model = step_10
```

Plot of model residuals against fitted values:

```{r}
birthweight_data_with_residual = add_residuals(birthweight_data, porposed_model)
birthweight_data_with_fittedvalue = add_predictions(birthweight_data, porposed_model)

fittedvalue_residual = birthweight_data_with_residual %>%
  mutate(pred = birthweight_data_with_fittedvalue$pred)

ggplot(fittedvalue_residual, aes(x = pred, y = resid)) +
  geom_point() +
  labs(x = "Fitted Value", y = "Model Residual")
```

Comment: heteroscedasticity exists is a violation of the Ordinary Least Squares assumptions. 

Compare the porposed_model with compare_model_1 and compare_model_2:

```{r}
compare_model_1 = lm(bwt ~ blength + gaweeks, data = birthweight_data)
compare_model_2 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight_data)
```

Make this comparison in terms of the cross-validated prediction error:

```{r}
cv_df = crossv_mc(birthweight_data, 100)

cv_df = cv_df %>%
  mutate(porposedmodel = purrr::map(train, ~porposed_model),
         model_1       = purrr::map(train, ~compare_model_1),
         model_2       = purrr::map(train, ~compare_model_2)) %>% 
  mutate(rmse_porposed = purrr::map2_dbl(porposedmodel, test, ~rmse(model = .x, data = .y)),
         rmse_model_1  = purrr::map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_model_2  = purrr::map2_dbl(model_2, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

Comment: the proposed model is the best among those three models.
